Optimized and Cost Considering Huffman Code For Biological Data Transmission

### 2015-01-22 Article/Article.tex
test

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\section{Results And Discussion}
\section{Conclusion}

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{lscape}
\usepackage[noend]{algpseudocode}

@@

\section{Results And Discussion}
\begin{landscape}
\begin{table*}
\small
\label{datas}
\caption{GABM for comparison for cost and number of bits of different approaches with different datasets}
\begin{center}
\begin{tabular}{c c c c c c c}
\toprule
$\textbf{Data sets}$ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{low cost considering  algorithm}& \multicolumn{2}{c}{Optimized algorithm}\\\hline
 & $\textbf{Cost}$	& $\textbf{Bits}$ &	$\textbf{Cost}$&	$\textbf{Bits	}$&$\textbf{Cost}$&	$\textbf{Bits}$
\\\hline
Mycobacterium smegmatis &76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
Amycolatopsis benzoatilytica &100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
Mycobacterium rhodesiae&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
Streptomyces bottropensis&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
Mycobacterium smegmatis. MC2&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
Mycobacterium smegmatis MKD8&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
Bradyrhizobium WSM471&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
Amycolatopsis thermoflava&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
Bacillus thuringiensis serovar thuringiensis&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
Bacillus thuringiensis Bt407&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
Pseudomonas aeruginosa 9BR&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
Bacillus thuringiensis serovar berliner&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
Bacillus thuringiensis serovar pakistani&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
Pseudomonas aeruginosa LES400&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
\bottomrule
\end{tabular}
\end{center}
\end{table*}
\end{landscape}

\section{Conclusion}
